### 2022-03-10 sections/papers.tex
Update papers.tex

\item{\small Cuevas, C. {\itshape et al.} ({\itshape forthcoming}). Public Service Motivation Among Chilean Public Employees. {\itshape Revista del CLAD Reforma y Democracia}, 80. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

@@

\begin{benumerate}{10}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

>>>>

\item{\small Cuevas, C. {\itshape et al.} ({\itshape forthcoming}). Public Service Motivation Among Chilean Public Employees. {\itshape Revista del CLAD Reforma y Democracia}, 80. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/p963q}{\textcolor{blue}{10.31235/osf.io/p963q}}}\vspace{1mm}

@@

\begin{benumerate}{10}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. Introduction. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}, 28. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/wud59}{\textcolor{blue}{10.31235/osf.io/wud59}}}\vspace{1mm}
